\model{Team Roles}

Decide who will be what role for today.
We will rotate roles throughout the course.

\begin{table}[h!]
\renewcommand{\arraystretch}{2}
\begin{tabular}{|p{0.5\linewidth}|}
\hline
Manager:   \ans{Helen Hu} \\
\hline
Presenter: \ans{Clif Kussmaul} \\
\hline
Recorder:  \ans{Chris Mayfield} \\
\hline
Reflector: \ans{Aman Yadav} \\
\hline
\end{tabular}
\end{table}

If you have only three people, one may serve as both manager and presenter.
If you have five team members, then assign two people to recorder or reflector.


\quest{12 min}

\Q What is the difference between \textbf{bold} and \textit{italics} on the role cards?

\begin{answer}
The bold points describe what the responsibilities are.
Examples of what that person would say are in italics.
\end{answer}


\Q Manager: invite each person to explain their role to the team.
Recorder: make sure all team members take notes by writing down key phrases next to the table above.

\vspace{1em}


\Q What responsibilities do two or more roles have in common?

\begin{answer}
Both the presenter and the recorder help the team reach consensus.
The manager and reflector both monitor how the team is working.
\end{answer}


\Q For each role, give an example of how someone observing your group would know that a person is \underline{not} doing their job well.

\begin{itemize}
\setlength\itemsep{1em}

\item Manager: \ans{The team is constantly getting behind.}

\item Presenter: \ans{The student doesn't know what to say.}

\item Recorder: \ans{Some team members aren't taking good notes.}

\item Reflector: \ans{The student never comments on team dynamics.}

\end{itemize}
