% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Classes and UML}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

When you define a class in Java, you are designing a new type of object.
Each object has its own copy of the variables and methods in the class.

\rolenames

\guide{
  \item Define the terms: attribute, method, constructor, scope.
  \item Implement non-static methods based on a UML diagram.
  \item Distinguish static, instance, parameter, and local variables.
}{
  \item Writing method signatures exactly as shown in a UML diagram. (Information Processing)
}{
\ref{die-class.tex} is primarily about introducing object-oriented vocabulary.
As you walk around, keep an eye on \ref{dievar}.
Some students may incorrectly write \texttt{int lucky}, and if that happens, have them re-read the text in the model.
For reporting out, quickly have presenters of neighboring teams compare their answers and ask questions as needed.

\ref{circle-class.tex} asks students to implement a \texttt{Circle} class, one method at a time.
Make sure they write the complete method definition, not just the method body.
After students complete \ref{circmain}, show \sol{Act10}{Circle.java} on the projector and step through the code beginning from \texttt{main}.
It may be helpful to use \href{https://cscircles.cemc.uwaterloo.ca/java_visualize/}{Java Visualizer} to illustrate how \texttt{Circle} objects are created.

\ref{variable-scope.tex} presents a slightly different circle implementation named \texttt{SwapCircle}.
Have students work through the first questions as quickly as possible so they can spend time on \ref{summary}.
You'll need about ten minutes at the end of class to walk students through the solution, again using Java Visualizer or a similar tool.

Key questions: \ref{dievar}, \ref{circmain}, \ref{summary}

Source files:
\src{Act10}{Die.java},
\src{Act10}{SwapCircle.java},
\src{Act10}{SwapDriver.java}
}

\input{die-class.tex}
\input{circle-class.tex}
\newpage
\input{variable-scope.tex}

\end{document}
