\model{Variable Scope}
% based on Model 1 of "Improved Scope" activity by Helen Hu

As a team, first review and discuss the \java{SwapCircle} and \java{SwapDriver} classes found at the end of the questions.
Then identify the \emph{scope} of each variable based on the table below.

\begin{center}
\small
\begin{tabular}{|L{95pt}|L{125pt}|L{115pt}|L{105pt}|}
\hline
\tr &
\tr \textbf{Where declared?} &
\tr \textbf{Where used?} &
\tr \textbf{Example} \\
\hline
\textbf{static variables} \par (``class variables'') &
declared outside of all methods (typically at the start of the class) &
anywhere in the class (or in other classes if also \java{public}) &
\java{circleCount} in the \java{SwapCircle} class \\
\hline
\textbf{instance variables} \par (``attributes'') &
declared outside of all methods (typically after any static variables) &
any non-static method (or in static methods when another object has been created) &
\java{radius} in the \java{SwapCircle} class \\
\hline
\textbf{parameters} &
declared inside the ()'s of a method signature &
anywhere within the method where they are declared &
\java{radius} in the \java{SwapCircle} constructor \\
\hline
\textbf{local variables} &
declared inside a method (or inside another block of code, like a \java{for} loop) &
anywhere within the method or code block after they are declared &
\java{temp} in the \java{swapInts} method \\
\hline
\end{tabular}
\end{center}


\quest{20 min}

\setlength{\defaultwidth}{37em}


\Q Identify one static variable from the \java{SwapCircle} class.
\begin{enumerate}
\item What is the name and purpose of the variable?
\\ \ans{\java{circleCount} -- tracks the number of \java{SwapCircle} objects that have been created} \\[-2em]

\item What is the scope of the variable?
\\ \ans{{\tt private static} -- it can be used anywhere within the \java{SwapCircle} class only} \\[-2em]

\item What is one example of somewhere it cannot be used?
\\ \ans{\tt SwapDriver.main} \\[-2em]

\end{enumerate}


\Q Identify one instance variable from the \java{SwapCircle} class.
\begin{enumerate}
\item What is the name and purpose of the variable?
\\ \ans{\java{radius} -- stores the radius of {\tt this} SwapCircle} \\[-2em]

\item What is the scope of the variable?
\\ \ans{{\tt private} and non-{\tt static} -- it can only be used in \java{SwapCircle} in non-static contexts} \\[-2em]

\item What is one example of somewhere it cannot be used?
\\ \ans{\tt SwapDriver.main} \\[-2em]
\end{enumerate}


\newpage

\Q Identify an example of where an instance variable is used within a static method.
\begin{enumerate}
\item In which method does this occur? \\[2pt]
\ans{\java{radius} is used in the \java{swapCircles} method} \\[-2em]

\item Why is the method able to access these instance variables, even though they are private? \\[2pt]
\ans{\java{swapCircles} belongs to the \java{SwapCircle} class} \\[-2em]

\item Explain how this method is not a violation of the rule that instance variables cannot be accessed inside a static method. \\[1ex]
\ans{You can't use {\tt this}.radius in a {\tt static} method, but it's okay to use \java{c1.radius}} \\[-2em]
\end{enumerate}


\Q Identify one parameter from the \java{SwapCircle} class.
\begin{enumerate}
\item What is the name and purpose of the variable? \\[2pt]
\ans{Possible answers include: \java{radius} (in the constructor), \java{x} and \java{y}, \java{c1} and \java{c2}} \\[-2em]

\item What is the scope of the variable? \\[2pt]
\ans{The variable exists throughout the entire method (but not other methods).} \\[-2em]

\item Where can the variable not be used? \\[2pt]
\ans{It can't be used in other methods, e.g., you can't refer to \java{x} in \java{swapCircles}.} \\[-2em]
\end{enumerate}


\Q Identify one local variable from the \java{SwapCircle} class.
\begin{enumerate}
\item What is the name and purpose of the variable? \\[2pt]
\ans{Possible answers include: \java{temp} and \java{r} (both used for swapping values)} \\[-2em]

\item What is the scope of the variable? \\[2pt]
\ans{The variable exists from when it's declared until the end of the method.} \\[-2em]

\item Where can the variable not be used? \\[2pt]
\ans{It cannot be used in other methods and/or before it has been declared.} \\[-2em]
\end{enumerate}


\Q \label{predict}
In the space below, predict the output of the \java{SwapDriver} program.
Why are the results different when swapping integers and swapping objects?

\begin{answer}[14em]
\begin{minipage}{190pt}

\begin{javaans}
BEFORE swap:
a = 7
b = 4
    Inside swapInts
    swapping integers 7 and 4
    finished swapping 4 and 7
AFTER swap:
a = 7
b = 4
\end{javaans}

\end{minipage}
\hspace{1em}
\begin{minipage}{290pt}

\begin{javaans}
BEFORE swap:
first = Circle(7)
second = Circle(4)
	Inside swapCircles
	swapping circles Circle(7) and Circle(4)
	finished swapping Circle(4) and Circle(7)
AFTER swap:
first = Circle(4)
second = Circle(7)
\end{javaans}

\end{minipage}
\begin{javaans}
This program created 2 circles
\end{javaans}
\end{answer}


\newpage

\begin{center}
\large\bf SwapCircle.java
\vspace{-4pt}
\end{center}

\jafile{SwapCircle.java}


\newpage

\begin{center}
\large\bf SwapDriver.java
\vspace{-4pt}
\end{center}

\jafile{SwapDriver.java}
