% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Recursive Drawings}
\author{Chris Mayfield}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

A recursive method is one that calls itself, usually with an increasing or decreasing argument.
In this activity, you will trace the execution of recursive methods that draw 2D graphics.

\rolenames

\guide{
  \item Use the Java 2D API to draw a repeating pattern on shapes.
  \item Explain how base cases and recursive calls affect execution.
  \item Identify similarities and differences in recursive methods.
}{
  \item Tracing the flow of execution using print statements. (Information Processing)
}{
Make sure that teams spend no more than five minutes on the first question of each model.
They will need time to set up and run the program, but they should use the questions to guide their discussion about the code.

Point out that \ref{model1.tex} is a warm-up to become familiar with the provided code.
There is no recursion yet, just standard Java 2D graphics.
Remind students that $(0,0)$ is at the upper-left corner of the \java{Drawing}.
Show students how to terminate the program and avoid leaving old \java{Drawing} windows open in the background.

%This activity includes questions to review Java-specific details about inheritance.
%On \ref{model2.tex}, help students avoid getting stuck on the \java{main} method.

At the beginning on \ref{model2.tex}, briefly explain how \java{VeeTree} inherits from \java{Drawing} and overrides the \java{draw()} method.
Because there is no constructor defined in \textit{VeeTree.java}, the the compiler automatically generates one that invokes \jans{super()}.
Recommend that students change the \jans{DELAY} constant to 250 ms for this drawing.

After \ref{model3.tex}, point out that it's very common for classes to have a public non-recursive method that calls a private recursive method.

Key questions: \ref{key1}, \ref{key2}, \ref{key3}

Source files:
\src{Act24}{Drawing.java},
\src{Act24}{Triangles.java},
\src{Act24}{VeeTree.java}
}

\input{model1.tex}
\newpage
\input{model2.tex}
\newpage
\input{model3.tex}

\end{document}
