% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Designing Classes}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

The \java{String} class provides methods for working with text.
The \java{Random} class provides methods for generating random numbers.
In this activity, you'll learn how to make your own classes that represent everyday objects.

\rolenames

\guide{
%  \item Discuss benefits of POGIL for student learning.
  \item Explain the purpose of constructor, accessor, and mutator methods.
  \item Implement the equals and toString methods for a given class design.
  \item Design a new class (UML diagram) based on a general description.
}{
  \item Identifying attributes and data types that model a real-world object. (Problem Solving)
}{
%The meta activities are designed to reestablish student buy-in later in the course.
%They are an opportunity to explain why you are using POGIL and how it benefits students.
%The figures and sample solutions are from Moog (2014), found in Chapter 8 of \href{https://dx.doi.org/10.7936/K7PN93HC}{Integrating Cognitive Science with Innovative Teaching in STEM Disciplines}.

\ref{common-methods.tex} begins with questions about constructors, getters, and setters.
Report out as soon as the majority teams have finished.
You may find it helpful to project the source code for {\it Color.java} while students work through the questions.
Reinforce the concept of immutable objects, and point out that the \java{String} class is designed this way.

The questions at the beginning of \ref{equals-tostring.tex} require students to understand the source code of \java{equals} and \java{toString}.
If this is the first time they have seen language features like \java{Object}, \texttt{instanceof}, and \java{String.format}, you might want to give a 5-minute lecture (but avoid giving away the answers).

When reporting out \ref{credit-card.tex}, have presenters write their designs on the board.
Compare the trade-offs of their different designs.
For example, to store credit card numbers some teams may use strings, others may use arrays of integers, and some may use a \texttt{long} variable (\texttt{int} won't work because of the range).

Key questions: \ref{key1}, \ref{key2}, \ref{key3}

Source files: \src{Act11}{Color.java}, \src{Act11}{Point.java}
}

%\input{../Meta/pogil-research1.tex}
%\input{../Meta/pogil-research2.tex}

\input{common-methods.tex}
\newpage
\input{equals-tostring.tex}
\vspace{1em}
\input{credit-card.tex}

\end{document}
