\documentclass[12pt]{article}

\title{Team Reflection}
\author{Dr. Chris Mayfield}
\date{Spring 2018}

\input{../cspogil.sty}

%------------------------------------------------------------------------------%
% half-page template

\newcommand{\half}[5]{%
\begin{minipage}[t][10cm]{\textwidth}

\begin{center}
\Large\bf #1's Report
\end{center}

\vspace{1ex}
Name: \hrulefill ~ Activity: \hrulefill

\vspace{1em}
\textbf{Evaluation} \\
\textit{On a 10-point scale (1=low 10=high), how well did you fulfill each responsibility?}

\vspace{1ex}
\begin{tabular}{l@{~~}l}
\blank & #2 \\
\blank & #3 \\
\blank & #4 \\
\end{tabular}

\vspace{1em}
#5

\end{minipage}}
%------------------------------------------------------------------------------%

\begin{document}

\half{Manager}
{Helps the team get started quickly and remain focused.}
{Takes care of time management; keeps an eye on the clock.}
{Makes sure that all voices in the team are heard and respected.}
{
\textbf{Muddiest Points} \\
\textit{What parts of today's activity (or last week's) is your team still confused about?}
}

\vfill

\half{Recorder}
{Records the important aspects of group discussions, insights, etc.}
{Guides consensus building process; helps team agree on responses.}
{Ensures that accurate revisions happen after class discussions.}
{
\textbf{Key Concepts} \\
\textit{Summarize the most important concepts and insights that your team learned today.}
}

\vfill

\half{Presenter}
{Communicates questions and clarifications with the instructor and other teams.}
{Ensures that all team members reach consensus before asking outside sources.}
{Presents conclusions of the team to the class, when requested by the instructor.}
{
\textbf{Reporting Out} \\
\textit{Which questions did you present to the class? Summarize your answers and comments.}
}

\vfill

\half{Reflector}
{Observes team dynamics and behavior with respect to the learning process.}
{Reports to the team periodically during the activity on how the team performs.}
{Be ready to report to the entire class about how well the team is operating.}
{
\textbf{Team Assessment} \\
\textit{What was a strength of your team today? How could your team improve next time?}
}

\end{document}
