\model{High-Level Languages}

In addition to adding the numbers from 1 to 10, this program prints (displays) the result on the screen using Standard I/O.

\begin{center}
\begin{minipage}[t]{186pt}
%\hrulefill

\textbf{Standard C} \\
(3rd Generation)

\begin{verbatim}
#include <stdio.h>

int main()
{
    int upper = 11;
    int sum = 1;
    int val = 2;

    while (val < upper)
    {
        sum = sum + val;
        val++;
    }

    printf("Sum = %d\n", sum);
}
\end{verbatim}
\end{minipage}
\hspace{1ex}\vline\hspace{1ex}
\begin{minipage}[t]{168pt}
%\hrulefill

\textbf{Python} \\
(4th Generation)

\begin{verbatim}




upper = 11
isum = 1
val = 2

while val < upper:

    isum = isum + val
    val = val + 1


print("Sum = " + str(isum))
\end{verbatim}
\end{minipage}
\end{center}


\quest{10 min}


\Q Compare the C code with the Python code.

\begin{enumerate}
\item Circle the lines of C code that were not present in \ref{low-level.tex}.
\ans[13em]{{\tt \#include} and {\tt printf}}

\item Which lines of C are not present (i.e., needed) in Python?
\ans[13em]{{\tt \#include} and {\tt int main}}

\item What punctuation used in C is not required in Python?
\ans[13em]{braces, semicolons, parens}

\end{enumerate}


\Q Without using braces, how does Python know which lines are part of the \verb|while| loop?

\begin{answer}
It uses indentation (and a colon to indicate the start of a new block).
\end{answer}


\Q Why does Python use the name \verb|isum| instead of \verb|sum|?
Hint: type \verb|sum| into a Python shell.

\begin{answer}
In Python, {\tt sum} is a built-in function.
It's best to avoid using these names for variables.
\end{answer}


\Q In Python, the \pyth{range} function can be used to generate a sequence of numbers.
Use a Python shell to answer this question.

\begin{enumerate}
\item What is the result of \pyth{list(range(5))}?  \ans{\tt [0, 1, 2, 3, 4]}
\item What is the result of \pyth{str(range(5))}? ~ \pans{'[0, 1, 2, 3, 4]'}
\item What do the \pyth{list} and \pyth{str} functions do?  \ans{Convert to list or string}
\item What is the result of \pyth{sum(range(5))}? ~ \ans{10}
\item What does the \pyth{sum} function do? \ans{It adds the given numbers}
\end{enumerate}


\Q Rewrite the entire program of \ref{\currfilename} using one line of Python code.
Hint: you'll need to use \verb|print|, \verb|str|, \verb|sum|, and \verb|range|.

\begin{answer}
\begin{pythans}
print("Sum = " + str(sum(range(11))))
\end{pythans}
\end{answer}


\Q Based on \ref{low-level.tex} and \ref{\currfilename}, what does it mean to be low-level vs high-level?

\begin{answer}
Low-level languages mimic the hardware and require a lot of simple instructions.
High-level languages focus more on the big picture, using fewer and more complex instructions.
\end{answer}
