% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Extending Classes}
\author{Chris Mayfield}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

The \java{extends} keyword allows you to define a new class based on an existing class.
This way, you can define new versions of classes without having to copy and paste their source code.

\rolenames

\guide{
  \item Explain what it means for one class to extend another.
  \item Summarize uses of the keywords \java{extends} and \java{super}.
  \item Write a new method for an existing Java library class.
}{
  \item Making conclusions based on IDE hints and program output. (Critical Thinking)
}{
This activity requires some prior knowledge of BigInteger and the \java{String.replace()} method.
All that's needed is a 10-minute mini lecture (e.g., using JShell) that shows how to create and add two BigIntegers, and how to find and replace strings.

BigInteger was originally chosen for this activity, because (1) it's a useful class in the Java library, and (2) it's not declared as \java{final} (so it can be extended).
The new feature this activity is adding to BigInteger is the ability to work with comma separators.

Highlight important aspects of the documentation for BigInteger.
For example, mention that BigInteger extends Number, which extends Object.
Notice the static constant fields.
In addition to the constructors, there is a static \java{valueOf} method.

Prevent students from spending too much time on \ref{count1} and \ref{count2}.
You can tell them the number of methods; they should be able to count the fields and constructors.
Introduce ``is a'' and ''has a'' terminology when reporting out.

Key questions: \ref{key1}, \ref{key2}, \ref{key3}

Source files: \src{Act19}{MyBigInt.java}
}

\input{model1.tex}
\newpage
\input{model2.tex}

\end{document}
