\model{Java Interfaces}

An interface is similar to an abstract class, except that all methods are automatically \java{public} and \java{abstract}.
Likewise, all fields are automatically \java{public}, \java{static}, and \java{final}.
These keywords are omitted in the interface definition.

\begin{quote}
\begin{javalst}
public interface Rechargeable {
    int MAX_CHARGE = 10;

    int getCharge();

    void recharge();
}
\end{javalst}
\end{quote}

Classes do not extend interfaces; they implement them:

\begin{quote}
\begin{javalst}
public class CellPhone implements Rechargeable {
    private int chargeLevel;
    private int volume;

    public CellPhone(int chargeLevel, int volume) {
        this.chargeLevel = chargeLevel;
        this.volume = volume;
    }

    public int getCharge() {
        return chargeLevel;
    }

    public void recharge() {
        chargeLevel = MAX_CHARGE;
    }

    public int getVolume() {
        return volume;
    }

    public void setVolume(int volume) {
        this.volume = volume;
    }

    public void makeCall() {
        System.out.println("Ring... Hello?");
    }
}
\end{javalst}
\end{quote}


\quest{15 min}

\Q What two methods are required by \java{Rechargeable}?

\begin{answer}[2em]
getCharge() and recharge()
\end{answer}


\Q Modify your \textit{ToyRobot.java} to implement the \java{Rechargeable} interface.
What changes did you need to make?

\begin{answer}[5em]
1. Add ``implements Rechargeable'' to the class definition. \\[1ex]
2. Define a getCharge method (copied it from CellPhone). \\[1ex]
3. Replaced 10 with \java{MAX_CHARGE} (constructor and recharge).
\end{answer}


\Q Consider the following \java{rechargeAll} method.
What type of objects are stored in the list?

\begin{javalst}
public static void rechargeAll(ArrayList<Rechargeable> list) {
    for (Rechargeable item : list) {
        item.recharge();
    }
}
\end{javalst}

\begin{answer}[3em]
It takes any type of Rechargeable object, such as CellPhone or ToyRobot.
\end{answer}


\Q \label{key3}
Consider the following \java{main} method.
Explain the significance of storing \java{ToyRobot} and \java{CellPhone} objects in the same \java{ArrayList} when calling \java{rechargeAll}.

\begin{javalst}
public static void main(String[] args) {
    ArrayList<Rechargeable> items = new ArrayList<>();
    items.add(new ToyRobot());
    items.add(new CellPhone(4, 5));
    rechargeAll(items);
}
\end{javalst}

\begin{answer}[5em]
The power of polymorphism through interfaces!
The rechargeAll method can operate on ToyRobots and CellPhones even though they are not related through inheritance.
\end{answer}


\Q Explain how an interface is like a contract.

\begin{answer}
An interface is a data type that is guaranteed to have specific methods.
Classes that implement an interface must provide those methods.
\end{answer}
