%Students likely won't have time to complete the CodingBat problems in \ref{stringMatch} and \ref{stringYak}, but they might continue working on them outside of class.
%Have teams outline the algorithms for these problems first, before writing Java syntax on paper.


\section*{Exercises}


\Q \label{stringMatch}
Discuss the \java{stringMatch} problem on the next page.
What three \java{String} methods will you need to solve it?
(If you have time during the activity, complete the method.)

\begin{answer}[3em]
\java{String.length} for the loop, and \java{String.substring} and \java{String.equals} for the comparison.
\end{answer}


\Q \label{stringYak}
Discuss the \java{stringYak} problem on the next page.
What two \java{String} methods will you need to solve it?
(If you have time during the activity, complete the method.)

\begin{answer}[3em]
\java{String.length} for the loop, and \java{String.charAt} to identify \chr{y} and \chr{k}.
\end{answer}


\newpage

[CodingBat] Given two strings, return the number of positions where they contain the same substring of length two. So \java{"xxcaazz"} and \java{"xxbaaz"} yields 3, since the \java{"xx"}, \java{"aa"}, and \java{"az"} substrings appear in the same place in both strings.

\medskip
\begin{javalst}
public static int stringMatch(String a, String b) {
\end{javalst}

\vspace{-1ex}
\begin{answer}[18em]
\begin{javaans}
    // figure which string is shorter
    int len = Math.min(a.length(), b.length());
    int count = 0;

    // look at both substrings starting at i
    for (int i = 0; i < len - 1; i++) {
        String aSub = a.substring(i, i + 2);
        String bSub = b.substring(i, i + 2);
        if (aSub.equals(bSub)) {
            count++;
        }
    }

    return count;
\end{javaans}
\end{answer}
\vspace{-1ex}

\begin{javalst}
}
\end{javalst}

\vfill

[CodingBat] Suppose the string \java{"yak"} is unlucky. Given a string, return a version where all the \java{"yak"} are removed, but the \java{'a'} can be any character. The \java{"yak"} strings will not overlap.

\bigskip

\java{stringYak("yakpak")} $\rightarrow$ \java{"pak"}

\java{stringYak("pikyik")} $\rightarrow$ \java{"pik"}

\java{stringYak("yak123ya")} $\rightarrow$ \java{"123ya"}

\medskip
\begin{javalst}
public static String stringYak(String str) {
\end{javalst}

\vspace{-1ex}
\begin{answer}[16em]
\begin{javaans}
    String result = "";

    for (int i = 0; i < str.length(); i++) {
        if (i + 2 < str.length() && str.charAt(i) == 'y'
                                 && str.charAt(i + 2) == 'k') {
            i = i + 2;
        } else {
            result += str.charAt(i);
        }
    }

    return result;
\end{javaans}
\end{answer}
\vspace{-1ex}

\begin{javalst}
}
\end{javalst}
