\model{ArrayList Methods}

Open the \href{https://docs.oracle.com/en/java/javase/11/docs/api/java.base/java/util/ArrayList.html}{ArrayList documentation} to answer questions about the following methods.
The data type ``\java{E}'' refers to the type of elements in the ArrayList (e.g., \java{Integer}).

\begin{center}
\begin{tabularx}{\linewidth}{|p{68pt}|p{154pt}|X|}
\hline
  \tr Return Type
& \tr Method
& \tr Description
\\ \hline
  \java{boolean}
& \java{add(E e)}
& Appends the specified element to the end of this list.
\\ \hline
  \java{void}
& \java{add(int index, E element)}
& Inserts the specified element at the specified position in this list.
\\ \hline
  \java{E}
& \java{get(int index)}
& Returns the element at the specified position in this list.
\\ \hline
  \java{E}
& \java{set(int index, E element)}
& Replaces the element at the specified position in this list with the specified element.
\\ \hline
  \java{int}
& \java{size()}
& Returns the number of elements in this list.
\\ \hline

\end{tabularx}
\end{center}



\quest{15 min}


\Q What value does the \java{add} method return?

\begin{answer}[2em]
\jans{true} (as specified by \jans{Collection.add(E)})
\end{answer}


\Q What value does the \java{set} method return?

\begin{answer}[2em]
the element previously at the specified position
\end{answer}


\Q What happens to existing elements when adding an element at a specified index?

\begin{answer}[3em]
Shifts the element currently at that position (if any) and any subsequent elements to the right (adds one to their indices).
\end{answer}


\Q What are the contents of \java{nums} after running the following code?

\begin{javalst}
ArrayList<Integer> nums;
nums = new ArrayList<Integer>();
nums.add(74);
nums.add(21);
nums.add(0, 11);
nums.set(1, 59);
\end{javalst}

\begin{answer}[2em]
[11, 59, 21]
\end{answer}


\newpage

\Q \label{key3}
The following program, found in \textit{Model3.java}, uses an array of ints.
Rewrite the program to use an ArrayList instead.

\vspace{1ex}

\begin{javalst}
import java.util.Arrays;

public class Model3 {

    public static void main(String[] args) {
        final int N = 4;
        int[] nums = new int[N];
        for (int i = 0; i < N; i++) {
            nums[i] = i + 1;
        }
        for (int i = 0; i < N; i++) {
            nums[i] *= 5;
        }
        System.out.println(Arrays.toString(nums));
    }

}
\end{javalst}

\begin{answer}[22em]
\begin{javaans}
import java.util.ArrayList;

public class Model3ans {

    public static void main(String[] args) {
        final int N = 4;
        ArrayList<Integer> nums = new ArrayList<Integer>();
        for (int i = 0; i < N; i++) {
            nums.add(i + 1);
        }
        for (int i = 0; i < N; i++) {
            nums.set(i, nums.get(i) * 5);
        }
        System.out.println(nums);
    }

}
\end{javaans}
\end{answer}
