% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Boolean Logic}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

The primitive data type \java{boolean} has two values: \java{true} and \java{false}.
Boolean expressions are built using \emph{relational operators} and \emph{conditional operators}.

\rolenames

\guide{
  \item Recognize the value of developing process skills.
  \item Evaluate boolean expressions with relational operators (<, >, <=, >=, ==, !=).
  \item Explain the difference between assignment (=) and equality (==) operators.
  \item Evaluate boolean expressions that involve comparisons with \&\&, ||, and !.
}{
  \item Evaluating complex logic expressions based on operator precedence. (Critical Thinking)
}{
The meta activity is ultimately about process skills and should help with student buy-in.
If you are using the \github{Handouts/role-cards-mayfield.pdf}{Role Cards}, have students look at the definitions on the reverse side.
Each activity targets specific ``process skill goals'' from these categories.
Point out that ``Technical skills'' is ranked tenth, after all the others.

At the beginning of \ref{relational.tex}, you might instruct students to check their work using JShell or a similar tool.
Give students about three minutes to fill in the table without using a computer.
If computers are not available, show them the actual results interactively on the projector.
Have teams discuss any of their predictions that were incorrect.

When reporting out, ask students to explain what \emph{expressions} are and how they differ from \emph{statements}.
Reinforce what it means to \emph{evaluate} an expression (i.e., compute a single value) versus \emph{execute} a statement (i.e., run an entire line of code).

During \ref{conditional.tex}, explain that the variables $p$ and $q$ are often used to represent logic values in discrete math.
Make sure students understand that ! is a \emph{unary} operator, and that \java{&&} and \java{||} are \emph{binary} operators.
Refer back to the meta activity to reinforce the importance of students communicating with each other as a team.

Key questions: \ref{key1}, \ref{key2}, \ref{key3}
}

\input{../Meta/employers.tex}
\input{relational.tex}
\input{conditional.tex}

\end{document}
