\documentclass[12pt]{article}

\title{Activity 5: Loops}
\author{Chris Mayfield and Helen Hu}
\date{July 2017}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Computers are often used to perform repetitive tasks.
Running the same statements over and over again, without making any mistakes, is something that computers do very well.

\guide{
  \item Explain what happens when re-assigning a variable.
  \item Identify the three main components of a while loop.
  \item Implement the factorial function using a for loop.
}{
  \item Tracing the execution of while/for loops and predict their final output. (Critical Thinking)
}{
TODO

Extension activity by Debra Duke:
Bring a couple of note cards labeled with a large 1 on the first and a large 2 on the second card.
Have all the students in the team put one hand behind their back, and then hand the cards to two members (student X gets the 1 and student Y gets the 2).
Ask them to exchange cards.
When they struggle, say ``What if you had a student Z who could help?''

When reporting out Model 2, have teams predict the answers to numbers Questions 11, 12, and 15.
Then execute the code and have them discuss their results, if incorrect.

On Question 22, students may forget to use a {\tt long} variable to store the factorial.
If time permits, show the output of the solution when {\tt fact} is declared as {\tt int}.
}

%TODO add flow charts for loops?

\input{assignment.tex}
%\newpage
\input{while-loops.tex}
\input{for-loops.tex}

\end{document}
