\model{Arrays and Loops}

The real power of arrays is the ability to process them using loops, i.e., performing the same task for multiple elements.
The standard form of iteration is as follows:

\begin{javalst}
    for (int i = 0; i < array.length; i++) {
       ... process array[i] ...
    }
\end{javalst}

For example:

\begin{javalst}
    // set all of the elements of x to -1.0
    double[] x = new double[100];
    for (int i = 0; i < x.length; i++) {
        x[i] = -1.0;
    }
    // sum the elements of scores
    int sum = 0;
    for (int i = 0; i < scores.length; i++) {
        sum += scores[i];
    }
\end{javalst}


\quest{15 min}


\Q What is the value of \java{array} and \java{accumulator} after the following iteration? Trace the loop by hand in the space below.

\begin{javalst}
int[] array = {5, 26, 13, 12, 37, 15, 16, 4, 1, 3};
int accumulator = 0;
for (int i = 0; i < array.length; i++) {
    if (array[i] % 2 == 1 && i + 1 < array.length) {
        array[i] *= -1;
        accumulator += array[i+1];
    }
}
\end{javalst}

\begin{answer}
\end{answer}


\newpage
\Q Implement the following method that creates and returns a \java{new} array.

\begin{javalst}
/**
 * Return a new array containing the pairwise maximum value of
 * the arguments. For each subscript i, the return value at [i]
 * will be the larger of x[i] and y[i].
 *
 * @param x an array of double values
 * @param y an array of double values
 * @return pairwise max of x and y; returns null if x.length
           != y.length or if either of the arrays is null
 */
public static double[] pairwiseMax(double[] x, double[] y) {
\end{javalst}

\vfill
\begin{javalst}
}
\end{javalst}


\Q Implement the following method that reads through two integer arrays.

\begin{javalst}
/**
 * Computes the final letter grade for a student. The labs are
 * worth 40% and the exams are worth 60%. All scores range from
 * 0 to 100, inclusive. Letter grades are assigned on the scale
 * A=90-100, B=80-89, C=70-79, D=60-69, F=0-59.
 *
 * @param labs the student's lab scores
 * @param exams the student's exam scores
 * @return letter grade 'A', 'B', 'C', 'D', or 'F'
 */
public static char finalGrade(int[] labs, int[] exams) {
\end{javalst}

\vfill
\begin{javalst}
}
\end{javalst}
