% Based on Model 2 of Activity 5 - Strings by Helen Hu

\model{String Methods}
\label{CS1/string-methods}

\begin{tabularx}{\linewidth}{|p{128pt}|p{72pt}|X|}
\hline
\tr Method & \tr Returns & \tr Description \\
\hline
\java{charAt(int)}          & \java{char}
  & Returns the char value at the specified index of \java{this} string. \\
%\hline
%\java{equals(Object)}       & \java{boolean}
%  & Compares \java{this} string to the specified object. \\
\hline
\java{indexOf(String)}      & \java{int}
  & Returns the index within \java{this} string of the first occurrence of the specified substring. \\
\hline
\java{length()}             & \java{int}
  & Returns the length of \java{this} string. \\
\hline
\java{substring(int, int)}  & \java{String}
  & Returns a new string that is a substring of \java{this} string (from \java{beginIndex} to \java{endIndex - 1}). \\
\hline
\java{toUpperCase()}        & \java{String}
  & Returns a copy of \java{this} string with all the characters converted to upper case. \\
\hline
\end{tabularx}

\vspace{1em}

Each method listed above is non-\java{static}.
That is, they have an implicit parameter named \java{this} that is passed automatically.


\quest{15 min}


\Q \label{strAPI} If \java{str} contains the string \java{"hello world"}, then what is the return value of the following method calls?

\begin{multicols}{2}
\begin{enumerate}
\item \java{str.charAt(6)} \ans{\chr{w}}
%\item \java{str.equals("hello")} \ans{\tt false}
\item \java{str.indexOf("ll")} \ans{2}
\item \java{str.length()} \ans{11}
\item \java{str.substring(4, 7)} \ans{\str{o w}}
\item \java{str.toUpperCase()} \ans{\str{HELLO WORLD}}
\end{enumerate}
\end{multicols}


\Q Explain what precedes the \java{.} (dot) operator in the expressions above.
What does it have to do with the keyword \java{this} in the model?

\begin{answer}
The variable containing the string precedes the dot operator. It is passed as the implicit {\tt this} parameter to the non-{\tt static} method.
\end{answer}


\Q How many arguments does each method call in \ref{strAPI} have?
(Hint: None of them have zero.)

\begin{multicols}{2}
\begin{enumerate}
\item \ans{2}
%\item \ans{2}
\item \ans{2}
\item \ans{1}
\item \ans{3}
\item \ans{1}
\end{enumerate}
\end{multicols}


\Q To compare strings, you must use either the \java{String.equals} or \java{String.compareTo} method.
Predict the output of the following code.

\begin{javalst}
String name1 = "Mark";
String name2 = "Ma" + "rk";
String name3 = "Mary";

// compare name1 and name2
if (name1 == name2) {
    System.out.println("name1 and name2 are identical");
} else {
    System.out.println("name1 and name2 are NOT identical");
}
\end{javalst}

\vspace{-3ex}
\begin{answer}[1em]
\tt \hspace{1em} name1 and name2 are identical ~ \normalfont Note: compiler optimization
\end{answer}

\begin{javalst}
// compare "Mark" and "Mark"
if (name1.equals(name2)) {
    System.out.println("name1 and name2 are equal");
} else {
    System.out.println("name1 and name2 are NOT equal");
}
\end{javalst}

\vspace{-3ex}
\begin{answer}[1em]
\tt \hspace{1em} name1 and name2 are equal
\end{answer}

\begin{javalst}
// compare "Mark" and "Mary"
if (name1.equals(name3)) {
    System.out.println("name1 and name3 are equal");
} else {
    System.out.println("name1 and name3 are NOT equal");
}
\end{javalst}

\vspace{-3ex}
\begin{answer}[1em]
\tt \hspace{1em} name1 and name3 are NOT equal
\end{answer}


\Q What is the difference between \emph{identical} and \emph{equal} in the previous question?

\begin{answer}
``Identical'' means the variables refer to the same \java{String} object.
``Equal'' means the strings have the same characters, in the \java{Arrays.equals} sense.
\end{answer}


%\Q Solve the \java{stringMatch} problem (see attached page) using \java{length} and \java{substring}.
