% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Data Types}
\author{Chris Mayfield and Stoney Jackson}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Java supports two main types of data: \emph{primitive types} like \java{int} and \java{double} that represent a single value, and \emph{reference types} like \java{String} and \java{Scanner} that represent more complex data.

\rolenames

\guide{
  \item Explain how using roles improves the team's success.
  \item Name Java's primitive data types and give examples of each one.
  \item Identify illegal assignment statements, and explain why they are illegal.
  \item Describe what it means for variables to store a reference to an object.
}{
  \item Providing feedback on how well other team members are working. (Teamwork)
}{
The meta activity reinforces the importance of roles.
Successful teams are able to accomplish all the tasks outlined on the \github{Handouts/role-cards-mayfield.pdf}{Role Cards}, and there's too many things for one person to keep track.
Ask the reflectors to pay special attention to their role during today's activity, and invite them at some point to report to share what they have observed.

On \ref{literals}, students may struggle with letters used in primitive values (i.e., F and L).
Rather than just say what everything means, direct students back to \ref{primitive-types.tex} and have them read out loud the type names.
%Explain that \texttt{float} is a floating-point data type, and ask students to guess where the name \texttt{double} comes from.
\ref{allowed} is good for report-out, allowing students to collectively develop a rule for when an assignment is allowed.
The solution files \sol{Act03}{Assign1.java} and \sol{Act03}{Assign2.java} are available for demonstration.
When reporting out, introduce the term \emph{literal}.

%It might be helpful to have a couple of examples handy to challenge their assumptions.
%But be careful, examples like \texttt{short x = 3; byte y = 3; char c = 3;} may open a can of worms.
%If these issues come up, you'll need to explain that \texttt{javac} will check the range of the value, and if it is acceptable, allow the assignment (i.e., \texttt{byte z = 255;} will fail).

\ref{reference-types.tex} introduces a technique for drawing memory diagrams to show the difference between primitive and reference types.
On \ref{twostrs}, have multiple teams draw their diagrams on the board.
Address misconceptions that arise (e.g., drawing multiple string objects).
It might be helpful at this point to direct students to \href{https://cscircles.cemc.uwaterloo.ca/java_visualize/}{Java Visualizer}, which draws similar diagrams.
Select the option ``Show String/Integer/etc objects, not just values'' for it to display references as arrows.

Key questions: \ref{allowed}, \ref{varval}, \ref{twostrs}

Source files: \src{Act03}{TaylorSwift.java}
}

\input{../Meta/disruptions.tex}
\newpage
\input{primitive-types.tex}
\newpage
\input{reference-types.tex}

\end{document}
