% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Loops and Iteration}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Computers are often used to perform repetitive tasks.
Running the same statements over and over again, without making any mistakes, is something that computers do very well.

\rolenames

\guide{
  \item Explain what happens when re-assigning a variable.
  \item Identify the three main components of a while loop.
  \item Rewrite a while loop as a for loop (and vice versa).
}{
  \item Tracing the execution of while/for loops and predict their final output. (Critical Thinking)
}{
\ref{assignment.tex} addresses two misconceptions about assignment: what happens when you reassign a variable, and how to swap two variables.
This understanding is essential for loop updates.

Optional warm-up activity:
{\small Bring a pair of note cards labeled with a large ``1'' on the first card and a large ``2'' on the second card.
Have all team members put one hand behind their back, and then hand the cards to two students (student $X$ gets the ``1'', and student $Y$ gets the ``2'').
Ask them to exchange cards, and when they struggle, ask them ``What if you had a student $Z$ who could help?''
(Credit: Debra Duke)}

When reporting out \ref{while-loops.tex}, have teams predict the answers to \ref{output}, \ref{value}, and \ref{do99}.
Then execute the code and have them discuss their results, if incorrect.
Consider stepping through the code with a debugger (on the projector) during report-out.

\ref{for-loops.tex} is a quick introduction to for loops.
Be sure to point out that the update step happens after the loop body.
If time permits, have students run their code on a computer to check their work.
You could also ask teams to discuss which loop syntax they like better, and why.

Key questions: \ref{compound}, \ref{do99}, \ref{loophead}

Source files:
\src{Act06}{Assignment.java},
\src{Act06}{WhileLoops.java},
\src{Act06}{ForLoops.java}
}

\input{assignment.tex}
\vfill
\input{while-loops.tex}
\vfill
\input{for-loops.tex}

\end{document}
