\documentclass[12pt]{article}

\title{Activity 6: Methods}
\author{Chris Mayfield}
\date{July 2017}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Java programs are organized into {\em classes}, each of which has one or more {\em methods}, each of which has one or more {\em statements}.
Writing methods allows you to break down a complex program into smaller blocks of reusable code.

\guide{
  \item Explain the syntax of a method declaration (parameters and return type).
  \item Apply methods from the Math class based on their documentation.
  \item Draw a diagram that shows the call stack at a given point of execution.
}{
  \item Tracing the execution of methods to determine the contents of memory. (Critical Thinking)
}{
This activity focuses on methods: declaration, invocation, and call semantics.
It also introduces the Math class to illustrate parameters vs arguments.
Model 3 builds on the previous activity for drawing diagrams and memory traces.

For questions 1 and 2, do a quick check of each teams' answer before they get too far along.
Some misread or misinterpret the question and/or don't get the difference between analyzing the code statically (e.g., how many lines of source code ...) vs dynamically (e.g., how many times ... when the program runs).

Questions 14 and 15 are good for reporting out, to reinforce the concepts of signature, parameters, and arguments.
Students often confuse printf by using string concatenation with the format string.

Quesiton 18 implicitly refers to Model 2 of the previous activity; you may need to remind students that memory diagrams simply include a box for each variable.

Have multiple teams draw their diagram for Question \#20 on the board, to compare different ways students think about this question.
Address misconceptions and be sure to show the correct solution.
}

\input{invoke-return.tex}
\input{method-declare.tex}
\input{stack-diagrams.tex}

\end{document}
