\documentclass[12pt]{article}

\title{Activity 8: Recursion}
\author{Chris Mayfield, Dee Weikle, and Helen Hu}
\date{July 2017}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Sometimes when solving a problem, we can compute the solution of a simpler version of the \emph{same problem}.
Eventually we reach the most basic version, for which the answer is trivial.

\guide{
  \item Identify the base case and recursive step of the factorial method.
  \item Trace a recursive method by hand and predict its final output.
  \item Explain what happens in memory when a method calls itself.
}{
  \item Interpreting mathematical definitions to gain insight on recursion. (Information Processing)
}{
This activity is a first introduction to recursion using two mathematical examples: factorial and summation.
Students learn how to read and trace recursive methods, not how to formulate recursive solutions to problems.

Be sure to point out that ! in mathematics means factorial, but ! in Java means NOT. It's unfortunately common for operators to have slightly different meanings in different languages.

It's important to let students wrestle with these difficult concepts and not give too much help on individual questions. Keep an eye on questions 1--4, and if a team is getting off track, have them compare answers with a neighboring team.

Report out on \#5 and \#8 by having teams write their answers on the board. Ideally there will be multiple (incorrect) answers, which will lead to a discussion. Then paste the code in \#5 into \href{http://pythontutor.com/java.html}{Java Visualizer} and step through the code as a live demo.

It's possible that Model 1 may take an additional 10--15 minutes, based on how long you report out. After \#9, introduce the term \textbf{stack overflow} and make the connection to the call stack visualization above.

Model 2 should move a bit faster than Model 1, since it's similar to factorial. Have presenters write their team's solution to \#16 on the board. Address misconceptions about variables, parameter passing, and return values.
}

\input{factorial.tex}
\input{summation.tex}

%\input{file-search.tex}

\end{document}
