% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Multiple Methods}
\author{Chris Mayfield}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Java programs are organized into \emph{classes}, each of which has one or more \emph{methods}, each of which has one or more \emph{statements}.
Writing methods allows you to break down a complex program into smaller blocks of reusable code.

\rolenames

\guide{
  \item Apply methods from the Math class based on their documentation.
  \item Explain the syntax of a method declaration (parameters and return type).
  \item Draw a diagram that shows the call stack at a given point of execution.
}{
  \item Tracing the execution of methods to determine contents of memory. (Critical Thinking)
}{
This activity will likely take students longer than they think it will.
Remind managers to keep track of the time and presenters to be ready to report out.
The recorder (or other team member) could read questions out loud to help with pacing.

\ref{invoke-return.tex} includes only void methods with no parameters, so that students may focus on the flow of execution.
For \ref{lines} and \ref{times}, do a quick check of each team's answer before they get too far along.
Some misread or misinterpret the question and/or don't get the difference between analyzing the code statically (i.e., how many lines) vs dynamically (i.e., how many times).

\ref{math-methods.tex} introduces a number of terms.
\ref{println} and \ref{printf} are good for reporting out to reinforce the concepts of \emph{signature}, \emph{parameters}, and \emph{arguments}.
In addition, they address a misconception: students often misuse \texttt{printf} by concatenating the arguments to the format string.

\ref{stack-diagrams.tex} builds on a previous technique for drawing diagrams and memory traces (from the Data Types activity).
You might need to remind students that memory diagrams simply include a small box to the right of each variable name.
Have multiple teams draw their diagram for \ref{drawing} on the board to compare different ways students think about this question.

Key questions: \ref{key1}, \ref{methsig}, \ref{drawing}

Source files:
\src{Act04}{Print.java},
\src{Act04}{CtoF.java},
\src{Act04}{Stack.java}
}

\input{invoke-return.tex}
\newpage
\input{math-methods.tex}
\newpage
\input{stack-diagrams.tex}

\end{document}
