\documentclass[12pt]{article}

\title{Activity 4: Boolean Logic}
\author{Chris Mayfield and Helen Hu}
\date{July 2017}

\input{../../cspogil.sty}

\begin{document}

\maketitle

The primitive data type \java{boolean} has two values: \java{true} and \java{false}.
Boolean expressions are built using \emph{relational operators} and \emph{conditional operators}.

\guide{
  \item Recognize the value of developing process skills.
  \item Evaluate boolean expressions with relational operators (<, >, <=, >=, ==, !=).
  \item Explain the difference between assignment (=) and equality (==) operators.
  \item Evaluate boolean expressions that involve comparisons with \&\&, ||, and !.
}{
  \item Evaluating complex logic expressions based on operator precedence. (Critical Thinking)
}{
This activity introduces relational and conditional operators with a focus on evaluating boolean expressions.
It also includes two case studies of students who cheated on assignments that were supposed to be done individually.

Model 1 refers specifically to DrJava, but it can be replaced with other IDEs.
Give students about five minutes to fill in the table without using a computer.
Then show them the actual results interactively (or in an example program).

When reporting out, ask students to explain what \textbf{expressions} are and how they differ from \textbf{statements}.
Reinforce what it means to \textbf{evaluate} expressions (i.e., compute a value) versus \textbf{execute} statements.

For Model 2, explain that the variables \textbf{p} and \textbf{q} are often used to represent logic values in discrete math.
Make sure students understand that ! is a unary operator, and that \java{&&} and \java{||} are binary operators.

Models 3 and 4 are based on true stories, unfortunately.
Each team should have a copy of the \github{Handouts/jmu-honor-code.pdf}{Honor Code} or your own institution's policy.
20 minutes are allocated, but in practice it can take much less time.
}

\input{employ-skills.tex}
\input{relational.tex}
\input{conditional.tex}

\end{document}
