\model{What Employers Want}

``What do employers look for when they are seeking new college graduates to take on jobs?
According to NACE's \textit{Job Outlook 2016} survey, they are looking for leaders who can work as part of a team.''
{\footnotesize \url{http://www.naceweb.org/s11182015/employers-look-for-in-new-hires.aspx}}

\begin{table}[h!]
\centering

{\bf Attributes employers seek on a candidate's resume}
\vspace{2pt}

\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|l|l|c|}
\hline
\tr & \tr Attribute   & \tr \% of respondents \\
\hline
1.  & Leadership                     & 80.1\% \\
\hline
2.  & Ability to work in a team      & 78.9\% \\
\hline
3.  & Communication skills (written) & 70.2\% \\
\hline
4.  & Problem-solving skills         & 70.2\% \\
\hline
5.  & Communication skills (verbal)  & 68.9\% \\
\hline
6.  & Strong work ethic              & 68.9\% \\
\hline
7.  & Initiative                     & 65.8\% \\
\hline
8.  & Analytical/quantitative skills & 62.7\% \\
\hline
9.  & Flexibility/adaptability       & 60.9\% \\
\hline
10. & Technical skills               & 59.6\% \\
\hline
\end{tabular}

%\vspace{1ex}
%\footnotesize
%Source: \textit{Job Outlook 2016}, National Association of Colleges and Employers
\end{table}
\vspace{-1em}


\quest{10 min}


\Q What is the relationship between the top two attributes employers seek?

\begin{answer}[3em]
Leadership implies working with other people, most likely as part of a team.
Working in teams is essential to developing leadership skills.
\end{answer}


\Q How is communication (written and verbal) related to problem-solving?

\begin{answer}[3em]
Solving problems in teams involves talking to other people and trying different approaches.
Writing solutions down is necessary to solidify the details and share them with others.
\end{answer}


\Q As a team, come up with a short description/example of each attribute.

\begin{quote}
\begin{multicols}{2}
1. \ans{leading a group of people} \\[1ex]
2. \ans{geting along well with others} \\[1ex]
3. \ans{writing and reading effectively} \\[1ex]
4. \ans{finding solutions creatively} \\[1ex]
5. \ans{speaking and listening effectively}

6. \ans{self-motivated to work hard} \\[1ex]
7. \ans{acting or taking charge early} \\[1ex]
8. \ans{analyzing data and reasoning} \\[1ex]
9. \ans{being able to handle change} \\[1ex]
10. \ans{computer/technology literacy}
\end{multicols}
\end{quote}


\Q Which of these skills do you expect to develop in this course? Why?

\begin{answer}[3em]
Ideally, all of them. Students will definitely learn technical computer programming skills.
But working in teams provides the opportunity to develop many other employable skills.
\end{answer}
