\documentclass[12pt]{article}

\title{Activity 7: Arrays}
\author{Chris Mayfield and Helen Hu}
\date{July 2017}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Programs often need to store multiple values of the same type, such as a list of phone numbers, or the names of your top 20 favorite songs.
Rather than create a separate variable for each one, we can store them together using an array.

\guide{
  \item Explain course policies about academic honesty.
  \item Declare and initialize array variables of primitive types.
  \item Draw a memory diagram of an array of reference types.
  \item Write a for loop that iterates the contents of an array.
}{
  \item Developing algorithms that loop through arrays to compute a result. (Problem Solving)
}{
\ref{case1.tex} and \ref{case3.tex} can be helpful to clarify policies and discuss what is appropriate collaboration vs cheating.
Each team will need a copy of the \github{Handouts/jmu-honor-code.pdf}{Honor Code} or your own institution's document.
Only 10 minutes are allocated for this discussion, but it could take more time.

\ref{array-syntax.tex} introduces arrays for the first time, with a focus on array syntax and memory diagrams.
Students learn about zero-based indexing array processing using loops.
Be sure to discuss \ref{arrayexp} and \ref{arraysta} when reporting out.
Students often confuse \emph{expressions} with \emph{statements}.
Explain how Java generally requires the \texttt{new} operator when creating arrays, except in the case of \ref{arraysta}.

In \ref{array-diagrams.tex}, explain that the \texttt{new} operator automatically zeros-out memory for the array.
Therefore, the default value will be 0 for integers, 0.0 for doubles, \texttt{null} for strings, etc.
These values should be present in the team's diagrams.
You may need to remind students that references (i.e., to string objects) are drawn with an arrow.

Students will have the most trouble with \ref{array-loops.tex}, particularly if writing code on paper.
One way to jump start the process is to report out before teams write their solution.
Give each team 2--3 minutes to develop an algorithm and have the presenter describe it to the class.
Then have students complete \ref{pairwiseMax} and \ref{finalGrade} as an exercise outside of class.
}

\input{../Honor/case1.tex}
\input{../Honor/case3.tex}
\input{array-syntax.tex}
\input{array-diagrams.tex}
\input{array-loops.tex}

\end{document}
