\model{Array Syntax}
% based on Model 1 of Activity 13 - TwoD Arrays by Helen Hu

An \emph{array} variable allows you to store multiple variables (of the same type).
Each value in an array is known as an \emph{element}.
The programmer must specify the \emph{length} of the array (the number of array elements).
Once the array is created, its length cannot be changed.

\begin{quote}
\begin{javalst}
char[] letterArray = {'H', 'i'};
System.out.println(letterArray[0]);          // outputs H
System.out.println(letterArray.length);      // outputs 2

double[] numberArray = new double[365];
System.out.println(numberArray[0]);          // outputs 0.0
System.out.println(numberArray.length);      // outputs 365
\end{javalst}
\end{quote}

Array elements are accessed by \emph{index} number, starting at zero:

\begin{quote}
\begin{tabular}{C{2em}C{2em}}
\hline
\multicolumn{1}{|c|}{\java{'H'}} &
\multicolumn{1}{ c|}{\java{'i'}} \\
\hline
\fs 0 & \fs 1 \\
\end{tabular}
\hspace{3em}
\begin{tabular}{C{2em}C{2em}C{4em}C{2em}}
\hline
\multicolumn{1}{|c|}{\java{0.0}} &
\multicolumn{1}{ c|}{\java{0.0}} &
\multicolumn{1}{ c|}{$\cdots$} &
\multicolumn{1}{ c|}{\java{0.0}} \\
\hline
\fs 0 & \fs 1 &   & \fs 364 \\
\end{tabular}
\end{quote}


\quest{15 min}


\Q Examine the results of the code.

\begin{enumerate}
\item What is the length of \java{letterArray}? \ans[5em]{2}
\item What is the length of \java{numberArray}? \ans[5em]{365}
\item What is the index of the element \java{'i'} in \java{letterArray}? \ans[5em]{1}
\item What is the index of the last element of \java{numberArray}? \ans[5em]{\java{364}}
\end{enumerate}


\Q Now examine the syntax of the code.

\begin{enumerate}
\item What are three ways that square brackets [] are used?

\vspace{-1ex}
\begin{answer}[4em]
1) To declare the type: {\tt double[]}

2) To specify the length: {\tt double[365]}

3) To access an element: {\tt numberArray[0]}
\end{answer}

\item In contrast, how are curly braces \{\} used for an array?

\vspace{-1ex}
\begin{answer}[2em]
To create an array with an initial set of values.
\end{answer}
\end{enumerate}


\Q \label{typeval}
What are the resulting type and value of the following expressions?
Show your work by writing the value of each array element in the space provided.

\begin{javalst}
int[] a = {3, 6, 15, 22, 100, 0};
double[] b = {3.5, 4.5, 2.0, 2.0, 2.0};
String[] c = {"alpha", "beta", "gamma"};
\end{javalst}

\begin{enumerate}
\item \java{a[3] + a[2]}
\hfill
~ Type:  \ans[4em]{\tt int}
~ Value: \ans[4em]{\tt 37}
\hspace{8em} \\
\ans[2em]{22} ~~~ \ans[2em]{15}

\item \java{b[2] - b[0] + a[4]}
\hfill
~ Type:  \ans[4em]{\tt double}
~ Value: \ans[4em]{\tt 98.5}
\hspace{8em} \\
\ans[2em]{2.0} ~~~ \ans[2em]{3.5} ~~~ \ans[2em]{100}

\item \java{c[1].charAt(a[0])}
\hfill
~ Type:  \ans[4em]{\tt char}
~ Value: \ans[4em]{\tt \qs{a}\qs}
\hspace{8em} \\
\ans[2em]{beta} ~ ~ ~ ~ ~ ~ ~ \ans[2em]{3}

\item \java{a[4] * b[1] <= a[5] * a[0]}
\hfill
~ Type:  \ans[4em]{\tt boolean}
~ Value: \ans[4em]{\tt false}
\hspace{8em} \\
\ans[2em]{100} ~~~ \ans[2em]{4.5} ~~ ~~~ \ans[2em]{0} ~~~ \ans[2em]{3}

\end{enumerate}


\vspace{0pt}

\comment{
As shown in \ref{typeval}, an array variable can be declared and initialized without using \java{new}.
However, to assign an array variable that was previously declared, \java{new} is required: \\
~~~~~~~~\java{a = new int[] \{3, 6, 15, 22, 100, 0\};} \\[-1ex]
~~~~~~~~\java{c = new String[] \{"alpha", "beta", "gamma"\};}
}


\Q \label{arraysta}
Write statements that declare and initialize variables for the following arrays.

\begin{enumerate}

\item
\begin{tabular}{|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|}
\hline
0 & 14 & 1024 & 127 & 3 & 5521 \\
\hline
\end{tabular}

\vspace{1ex}
\ans[35em]{\tt int[] a = \{0, 14, 1024, 127, 3, 5521\};}

\item
\begin{tabular}{|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|}
\hline
3.23 & 1.52 & 4.23 & 32.5 & 2.45 & 5.23 & 3.33 \\
\hline
\end{tabular}

\vspace{1ex}
\ans[35em]{\tt double[] b = \{3.23, 1.52, 4.23, 32.5, 2.45, 5.23, 3.33\};}

\end{enumerate}


\Q \label{arrayexp}
Write statements that assign the following arrays to variables you declared in \ref{arraysta}.

\begin{enumerate}

\item
\begin{tabular}{|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|}
\hline
0 & 14 & 1024 & 127 & 3 & 5521 \\
\hline
\end{tabular}

\vspace{1ex}
\ans[35em]{\tt a = new int[] \{0, 14, 1024, 127, 3, 5521\}}

\item
\begin{tabular}{|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|C{3em}|}
\hline
3.23 & 1.52 & 4.23 & 32.5 & 2.45 & 5.23 & 3.33 \\
\hline
\end{tabular}

\vspace{1ex}
\ans[35em]{\tt b = new double[] \{3.23, 1.52, 4.23, 32.5, 2.45, 5.23, 3.33\}}

\end{enumerate}
