% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Arithmetic Operators}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Now that you've written a few programs, let's take a step back and discuss how to do basic arithmetic.
The behavior of Java operators (+, -, *, /, \%) depends on the type of data you have.

\rolenames

\guide{
  \item Summarize the benefits of working as a team.
  \item Evaluate Java expressions that use the \% operator with integers.
  \item Explain the difference between integer and floating-point division.
  \item Identify operator precedence for addition, division, and assignment.
}{
  \item Recognizing mathematical operations based on tables. (Information Processing)
}{
This activity focuses on integer vs floating-point division and operator precedence.
Students should understand how to declare and assign variables before completing this activity.
The meta activity at the beginning reinforces the idea of working together as a team.

\ref{mints} refers to the instructor hypothetically giving mints to teams to divide among themselves.
Consider bringing real mints to build rapport with the class.
You can use other small objects like paperclips.
When reporting out, introduce the terms \emph{remainder operator}, \emph{modulo operation}, and \emph{modulus}.
Explain that ``x \% y'' is pronounced ``x mod y''.

On \ref{dividing-numbers.tex}, you may need to point out (after students work for a while) that it makes no difference whether a floating-point number ends with a zero.
In other words, \java{4.} is the same value as \java{4.0}.
%
For \ref{intdiv}, have at least 2--3 teams share their answers with the class to encourage different ways of thinking about the concepts (and how to put them into words).

On \ref{order-operations.tex}, help students understand that assignment is an operation (in contrast to the equals sign in mathematics).
At the end of the activity, invite teams to discuss what the \emph{assignment operation} is in terms of what computer hardware does.

Key questions: \ref{modoper}, \ref{intdiv}, \ref{key3}
}

\input{../Meta/group-vs-team.tex}
\input{modulo-operator.tex}
\newpage
\input{dividing-numbers.tex}
\input{order-operations.tex}

\end{document}
