% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Introduction to Java}
\author{Chris Mayfield and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

In this course, you will work in teams of 3--4 students to learn new concepts.
This activity will introduce you to the process.
We'll also take a first look at how to store data in Java programs.

%\rolenames

\guide{
  \item Describe the responsibility of each team role.
  \item Identify components of the "hello world" program.
  \item Write Java code to declare int and double variables.
  \item Explain what it means to assign a value to a variable.
}{
  \item Leveraging prior knowledge and experience of other students. (Teamwork)
}{
This activity is designed for the first day or week of CS1.
There are no prerequisites.
During this activity, it's important to explain/model the instructor's role in an active learning classroom.
For large classes, it may take a bit longer than expected to organize teams.

The meta activity refers to \github{Handouts/role-cards-mayfield.pdf}{Role Cards}, which ideally should be printed out on a different color of card stock (one set per team).
You might want to have each team complete a \github{Handouts/team-report.pdf}{Team Report} at the end of this activity.

One strategy for reporting out \ref{hello-world.tex} is to have presenters of nearby teams swap answers and discuss any differences.
Introduce the terms \emph{documentation} (see \ref{javadoc}) and \emph{newline} (see \ref{println}).

Questions that ask students to explain (or to describe) are good for reporting out.
It's important that teams hear multiple perspectives on these concepts.
Introduce the terms \emph{data type} and \emph{operator}, and point out that \emph{assignment} is not the same as \emph{equality}.

On \ref{assignment.tex}, it may be necessary to explain that there are only two variables.
The boxes show the state of memory over time, as the corresponding statements are executed.

Key questions: \ref{javadoc}, \ref{vardecl}, \ref{xgets}

Source files: \src{Act01}{HelloWorld.java}
}

\input{../Meta/team-roles.tex}
\input{hello-world.tex}
\input{variables.tex}
\smallskip
\input{assignment.tex}

\end{document}
