% Based on Model 1 of "Activity 02 Declaration" by Helen Hu

\model{Variables}
\label{variable}

Most programs store and manipulate data, and we use \textit{variables} to give the data meaningful names.
The following code \emph{declares} and \emph{assigns} three variables.
Each variable is stored in the computer's memory, represented by the boxes on the right.

\vspace{1em}
\begin{minipage}[t]{0.45\textwidth}

\begin{center}
\textbf{Java code}
\end{center}

\begin{javabox}
int dollars;
int cents;
double grams;

dollars = 1;
cents = 90;
grams = 3.5;
\end{javabox}

\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}

\begin{center}
\textbf{Computer memory}
\end{center}

\begin{tabular}{R{50pt}|C{20pt}|}
\cline{2-2}
\java{dollars} & \java{1} \\
\cline{2-2}
\end{tabular}

\vspace{1em}

\begin{tabular}{R{50pt}|C{20pt}|}
\cline{2-2}
\java{cents} & \java{90} \\
\cline{2-2}
\end{tabular}

\vspace{1em}

\begin{tabular}{R{50pt}|C{20pt}|}
\cline{2-2}
\java{grams} & \java{3.5} \\
\cline{2-2}
\end{tabular}

\end{minipage}


\quest{10 min}


\Q Identify the Java \textbf{keyword} used in a variable declaration to indicate

\begin{enumerate}
\item an integer: \ans{int}
\item a real number: \ans{double}
\end{enumerate}


\Q Consider numbers of dollar bills, cents, and grams.
Which of these units only makes sense as an integer, and why?

\begin{answer}
Cents makes sense (ha ha) only as an integer, because at the end of the day, you can't pay with a fractional amount. (It is possible to make a similar argument for dollars, but not for grams.)
\end{answer}


\Q What would you expect the following statements to print out?

\begin{enumerate}
\item \java{System.out.println(dollars);} \ans{1}
\item \java{System.out.println(cents);} \ans{90}
\item \java{System.out.println(grams);} \ans{3.0}
\end{enumerate}


\Q What do you think the purpose of a variable declaration is?

\begin{answer}
It tells the computer how to interpret and display the value.
\end{answer}


\Q Consider the statement: ~ \java{cents = dollars;}

\begin{enumerate}

\item Compare this code to lines 5--7 in \ref{variable-declare}.
What value do you think cents and dollars will have after running this statement?

\ans{The variable \java{cents} will be 1, and \java{dollars} will remain unchanged.}

\item Which side of the equals sign (left or right) was assigned a new value?
\ans{The left side.}

\end{enumerate}


\Q Examples of Java operators include \java{+} and \java{-}; they describe an operation to be executed (e.g., addition or subtraction).

\begin{enumerate}

\item Do you consider the equals sign in Java an operator (an operation to be executed)?
\\ If so, explain the operation. If not, explain why not.

\ans{Yes; it executes the assignment operation which stores a value in memory.}

\item Do you consider the equals sign in mathematics an operator (an operation to be executed)?
\\ If so, explain the operation. If not, explain why not.

\ans{No; it simply states the proposition that two values are equal.}

\end{enumerate}


\Q In your own words, explain how you should read the \java{=} sign in Java.
For example, the Java statement ~ \java{x = a + b;} ~ should be read as ``x \_\_\_\_\_ a plus b.''

\begin{answer}
Answers may include ``x \emph{gets} a plus b'', ``x \emph{becomes} a plus b'', etc.
\end{answer}
