% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{File Input/Output}
\author{Chris Mayfield}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Most data is stored in files, not input by the user every time.
In this activity, you'll learn the basics of reading and writing plain text files.

\rolenames

\guide{
  \item Parse user input and string objects using a \java{Scanner}.
  \item Read a text file line by line, and extract data from it.
  \item Create a new text file, and output several lines to it.
}{
% \item Justifying answers based on the results of an experiment. (Critical Thinking)
  \item Reading Java API documentation to explore a class. (Information Processing)
}{
\ref{model1.tex} is an opportunity to introduce \java{System.in} and \java{System.out} as files.
In that way, students have been doing file I/O since Hello World.

On \ref{run1}, if the \textsf{Ctrl+D} key doesn't work, have students click the editor window and then click back to the Console window.
That should reset the Console input to recognize \textsf{Ctrl+D} again.
Students might confuse their own input as part of the program's output.
Make sure they don't have two copies of each line in their answer.

At the end of \ref{model2.tex}, compare answers for \ref{FNF} and \ref{key2}.
Discuss how to handle \java{FileNotFound} exceptions (e.g., print a stack trace, exit with an error code, or ask the user to try again).
Remind students of the difference between \java{next()} and \java{nextLine()}.

During \ref{model3.tex}, have students open their \textit{results.tsv} file both in a text editor and a spreadsheet application.
Discuss the file format and how it's displayed in each application.

Key questions: \ref{key1}, \ref{key2}, \ref{key3}
\hspace{1em}
Sample solution: \sol{Act16}{IMDb.java}

Source files: \src{Act16}{ScannerDemo.java}, \src{Act16}{title2020.tsv}
}

\input{model1.tex}
\newpage
\input{model2.tex}
\newpage
\input{model3.tex}

\end{document}
