% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Recursive Methods}
\author{Chris Mayfield, Dee Weikle, and Helen Hu}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

Sometimes when solving a problem, we can compute the solution of a simpler version of the {\it same problem}.
Eventually we reach the most basic version, for which the answer is trivial.

\rolenames

\guide{
  \item Identify the base case and recursive step of the factorial method.
  \item Trace a recursive method by hand and predict its final output.
  \item Explain what happens in memory when a method calls itself.
}{
  \item Evaluating mathematical sequences to gain insight on recursion. (Information Processing)
}{
This activity is a first introduction to recursion using two mathematical examples: factorial and summation.
Students learn how to read and trace recursive methods, not how to formulate recursive solutions to problems.
Let students wrestle with these difficult concepts, and don't give too much help on individual questions.

Keep an eye on questions 1--3, and if a team is getting off track, have them compare answers with a neighboring team.
You may need to point out that $!$ in mathematics means \emph{factorial}, but \java{!} in Java means \emph{not}.
It's unfortunately common that operators have slightly different meanings in different languages.

Report out on \ref{factjava} and \ref{output} by having teams write their answers on the board.
Ideally there will be slightly different (incorrect) answers, which will lead to a discussion.
Paste \textit{Recursion.java} into \href{https://cscircles.cemc.uwaterloo.ca/java_visualize/}{Java Visualizer} and step through the code as a live demo.
After \ref{stackover}, introduce the term \emph{stack overflow} and make the connection to the \emph{call stack} visualization in Java Visualizer.

Depending on how long you report out, \ref{factorial.tex} could take an additional 5--10 minutes.
\ref{summation.tex} should move a bit faster, since summation is almost identical to factorial.
Invite presenters to write their team's solution to \ref{diagram} on the board.
Address any misconceptions about variables, parameter passing, and return values.

Key questions: \ref{key1}, \ref{stackover}, \ref{diagram}

Source files: \src{Act08}{Recursion.java}
}

\input{factorial.tex}
\newpage
\input{summation.tex}

\end{document}
