\section*{Meta Activity: What Employers Want}

The following data is from the \textit{Job Outlook 2019} survey by the National Association of Colleges and Employers (NACE). A total of 172 organizations responded to the survey.

\begin{table}[h!]
\centering

{\bf Attributes Employers Seek on a Candidate's Resume}
\vspace{1ex}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|l|c|}
\hline
\tr Attribute                  & \tr \% of respondents \\
\hline
Ability to work in a team      & 78.7\% \\
\hline
Analytical/quantitative skills & 71.9\% \\
\hline
Communication skills (verbal)  & 67.4\% \\
\hline
Communication skills (written) & 82.0\% \\
\hline
Detail-oriented                & 59.6\% \\
\hline
Initiative                     & 74.2\% \\
\hline
Leadership                     & 67.4\% \\
\hline
Problem-solving skills         & 80.9\% \\
\hline
Strong work ethic              & 70.8\% \\
\hline
Technical skills               & 59.6\% \\
\hline
\end{tabular}

\vspace{1ex}
{\footnotesize Source:~~\url{https://www.naceweb.org/talent-acquisition/candidate-selection/}}
\end{table}
\vspace{-1em}


\quest{10 min}


\Q What are the top three attributes that employers look for on a resume?

\begin{itemize}[itemsep=1ex]
\item \#1: \ans{Communication skills (written)}
\item \#2: \ans{Problem-solving skills}
\item \#3: \ans{Ability to work in a team}
\end{itemize}

\vspace{-1ex}


\Q Describe the process your team used to answer to the previous question.

\begin{answer}[3em]
We searched the table for the highest three percentages and then made sure that we all had the same answers.
(Note that searching/sorting involves comparison, which is the next model.)
\end{answer}


\Q How is communication (written and verbal) related to problem solving and teamwork?

\begin{answer}[3em]
Solving problems in teams involves talking to other people and trying different approaches.
Writing solutions down is necessary to solidify the details and share them with others.
\end{answer}


\Q How does the team-based learning approach in this class help you develop these skills?

\begin{answer}[3em]
POGIL activities provide an opportunity to develop these skills during class.
Ideally, students will learn these skills both in the classroom and in other activities like clubs and internships.
\end{answer}
