% comment out for student version
\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Linked Structures}
\author{Chris Mayfield and Dee Weikle}
\date{Summer 2021}

\input{../../cspogil.sty}

\begin{document}

\maketitle

The \textit{Java Collections Framework} provides many useful interfaces and implementations (classes). %, and algorithms (methods).
They all serve the same purpose: to store a collection of objects.
Each type of collection has its trade-offs, and there is no one ``best solution'' for every storage problem.
%If arrays were good enough, Java wouldn't need a collections framework.

%\medskip
%Today you will learn one of the most fundamental concepts of data structures: whether to store elements in contiguous memory locations (arrays), or link elements together using references.

\guide{
  \item Show the contents of a List after adding and removing elements.
  \item Summarize performance trade-offs for ArrayList and LinkedList.
}{
  \item Making connections between list diagrams and source code. (Information Processing)
}{
\ref{list-interface.tex} should be a quick review based on students' prior experience with \java{ArrayList}s.
Report out \ref{listtable} by projecting (or drawing) the table on the board and asking presenters to fill in rows.

Within the first five minutes of \ref{array-lists.tex}, report out on \ref{arrayopers} to make sure students understand what is meant by ``operations'' (assignments).
Note that \ref{linked-lists.tex} continues this idea to include assigning references.
Avoid discussing low-level details such as memory management and object overhead.
After reporting out \ref{ArraysAreBad} and \ref{LinksAreBad}, run one of them for about 10 seconds.
Then terminate the program, change the list type in \java{main}, and rerun the program.

At the end of \ref{linked-lists.tex}, it is helpful to show the \github{CS1/Act18/util}{Java library source code} for List, ArrayList, and LinkedList.
Help students make connections from the models in this activity to their actual implementation in Java.
For example, you can display the private methods of LinkedList and ask presenters to discuss their team's answer to \ref{LinksAreBad}.

Key questions: \ref{key1}, \ref{key2}, and \ref{key3}

\textbf{Acknowledgements:} The figures and source code in this activity are based on presentation materials by Nathan Sprague, and \ref{list-interface.tex} is based on a Lists activity by Clif Kussmaul.
}

\input{list-interface.tex}
\clearpage
\input{array-lists.tex}
\clearpage
\input{linked-lists.tex}

\end{document}
